Catchy Title Goes Here

### 2018-06-20 Paper/paper.tex
updated results text for Figure 4

The age distribution of measles cases was taken from individual case-reporting for DRC reported to the World Health Organization (WHO) between 2011-2017. During this time period, 33098 suspected measles cases were reported, of which 5495 were classified as lab-confirmed by the presence of IgM measles antibodies and 13858 were classified  as epidemiologically linked because they occurred close in time and space to a lab confirmed case.  For each suspected case we extracted the age, in months, and the province in which the case was recorded. Because the age of many cases was binned to the year (e.g. recorded as 24 or 36 months) we rounded all cases up to the nearest year; thus cases were binned into 1 year age classes following the convention (0,1],(1,2], etc. 
\subsection{Comparing Data and Inference \label{subsec:Comp}}
A standard approach for interpreting the results of Bayesian inference would be inspecting the posterior distributions for the model parameters. But the parameters of our model are not, in themselves, particularly interesting - it is the inferred seroprevalence, case distribution, and vaccination probability that we wish to compare with the data. To do this, we generate the posteriors on $\{\eta_f, \alpha_f, \beta_f, \gamma, \eta_v, \alpha_v, \beta_v\}$ as described, and then draw from these posteriors to generate the seroprevalence, case, and vaccination curves as laid out in Sec.~\ref{subsec:CompetingRates}. Because the vaccine efficacy, $\gamma$, is of interest on its own, we also examine the posterior distributions for this parameter in detail.

@@

@@

Finally, in Fig.~\ref{fig:riskrank}, we assess what we call the `risk' inferred for with each province, which we define as
\begin{equation}
r = \int_0^{10} \mathrm{foi}(a) da,
\end{equation}
 or the force of infection integrated from 0 to $10$ years. We calculate the foi using serology data only (left-most point), case and vaccination data only (middle point), and all three datasets (right-most point), and show the integrated values in Fig.~\ref{fig:riskrank}. The provinces are color-coded as throughout this section, and a dashed line is drawn to guide the eye between the results for different datasets. Below the points, we show maps of the DRC with each province colored according to the risk level, with dark blue being lowest risk and yellow highest. The most obvious conclusion from this plot is that the inclusion of case and vaccination data leads us to drastically increase our assessment of risk in many provinces. Interestingly, the inclusion of serology data does not make a significant difference in the calculated risk. The information from serology data seems to be most useful for inferring vaccine efficacy, rather than force of infection.

>>>>

The age distribution of measles cases was taken from individual case-reporting for DRC reported to the World Health Organization (WHO) between 2011-2017. During this time period, 33098 suspected measles cases were reported, of which 5495 were classified as lab-confirmed by the presence of IgM measles antibodies and 13858 were classified  as epidemiologically linked because they occurred close in time and space to a lab confirmed case.  For each suspected case we extracted the age, in months, and the province in which the case was recorded. Because the age of many cases was binned to the year (e.g. recorded as 24 or 36 months) we rounded all cases up to the nearest year; thus cases were binned into 1 year age classes following the convention (0,1],(1,2], etc.

\subsection{Comparing Data and Inference \label{subsec:Comp}}
A standard approach for interpreting the results of Bayesian inference would be inspecting the posterior distributions for the model parameters. But the parameters of our model are not, in themselves, particularly interesting - it is the inferred seroprevalence, case distribution, and vaccination probability that we wish to compare with the data. To do this, we generate the posteriors on $\{\eta_f, \alpha_f, \beta_f, \gamma, \eta_v, \alpha_v, \beta_v\}$ as described, and then draw from these posteriors to generate the seroprevalence, case, and vaccination curves as laid out in Sec.~\ref{subsec:CompetingRates}. Because the vaccine efficacy, $\gamma$, is of interest on its own, we also examine the posterior distributions for this parameter in detail.

@@

We also assess an additional measure of the `infection risk' inferred for each province, which we define as
\begin{equation}
r = \int_0^{10} \mathrm{foi}(a) da,
\end{equation}
 or the force of infection integrated from 0 to $10$ years.  Thus, this is an aggregate measure of the total infection risk up to age 10. We calculate this infection risk using  case and vaccination data only, and all three datasets. In addition we calculate this measure using the model fit to the serology data alone (without case or vaccination coverage data).  This latter measure reflects the estimate one would make if inference were based only on the serosurvey of children between the ages of 5-59 months.

@@

%Finally, in Fig.~\ref{fig:riskrank}, we assess what we call the `risk' inferred for with each province, which we define as
%\begin{equation}
%r = \int_0^{10} \mathrm{foi}(a) da,
%\end{equation}
% or the force of infection integrated from 0 to $10$ years. We calculate the foi using serology data only (left-most point), case and vaccination data only (middle point), and all three datasets (right-most point), and show the integrated values in Fig.~\ref{fig:riskrank}. The provinces are color-coded as throughout this section, and a dashed line is drawn to guide the eye between the results for different datasets. Below the points, we show maps of the DRC with each province colored according to the risk level, with dark blue being lowest risk and yellow highest. The most obvious conclusion from this plot is that the inclusion of case and vaccination data leads us to drastically increase our assessment of risk in many provinces. Interestingly, the inclusion of serology data does not make a significant difference in the calculated risk. The information from serology data seems to be most useful for inferring vaccine efficacy, rather than force of infection.

To give a simple summary of the marginal benefit of serology data, we compare estimates of the integrated FOI below 10 years of age from the model fit to age-specific case incidence and vaccination coverage data, to the model including these data plus serological data.  For comparison, we also present the integrated FOI below 10 yars of age when fitting the model to the serological data from the DHS alone.  Using the serology data alone, the estimated integrated FOI is relatively low for all provinces; this result is not surprising as the DHS survey only included data below 59m of age and thus does not provide information for estimating the additional FOI above 59 months of age.  The inclusion of the case data results in higher estimates of the integrated FOI in 7 of 11 provinces.  Notably, while the absolute value of the integrated FOI changes for the full model, including age-specific case, vaccination coverage, and serological data, the rank order does not change relative to the model based on only case and vaccination coverage data.
